---
title: "Lab 2: Motion of the Glider"
output:
  html_document: default
  pdf_document: default
date: "6/1/2020"
---

```{r , include=FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```
# Lab2: Position, Velocity, and Acceleration

## Part1: Motion of the glider 

Mass of the glider, m= 0.80 kg and the strenth of fan force was selected to level 3.

### Data
```{r}
time <- seq(0,0.9, by=0.1)
Position<- c(0,0.02,0.06, 0.115, 0.19, 0.29, 0.4, 0.53, 0.68, 0.84)
Velocity <- c(0,0.3,0.475, 0.65, 0.875, 1.05, 1.2, 1.4, 1.55,NA)
```

### Creating a data table
```{r}
data <- data.frame(time, Position, Velocity)
data
```

### Plotting Position vs. Time
```{r}
plot(data$time, data$Position,main="Position vs. Time", xlab="Time", ylab="Position" )
```

### Plotting Velocity vs. Time
```{r}
fit2<- lm(Velocity~time, data)
plot(data$time, data$Velocity, main="Velocity vs. Time", xlab="Time", ylab="Velocity")
abline(fit2)
```

### Fitting the linear regression model and extracting the coefficients
```{r}
summary(fit2)
summary(fit2)$coef
slope <- round(summary(fit2)$coef[2,1],3)
intercept<- round(summary(fit2)$coef[1,1],3)
errorintercept <- round(summary(fit2)$coef[1,2],3)
errorslope <- round(summary(fit2)$coef[2,2],3)
```




## Plots using ggplot
### Position vs. Time
```{r, message=FALSE, warning=FALSE}
g1<- ggplot(data, aes(x=time, y=Position))+
        geom_point(size = 2, colour = "red", alpha=0.5)+
        xlab("Time")+
        ylab("Position") +
        ggtitle("Position vs. time") 
        
        
g1
```

###Velocity vs. Time
```{r, message=FALSE, warning=FALSE}
g2 <- ggplot(data, aes(x=time, y=Velocity))+
        geom_smooth(method = "lm", colour = "black") + 
        xlab("Time")+
        ylab("Velocity") +
        ggtitle("Velocity vs. time") + 
        geom_point(size = 2, colour = "blue", alpha=0.5)
        
g2
```
$$ v_o= `r intercept` \pm `r errorintercept`  \frac{m}{s} $$
$$ a= `r slope` \pm `r errorslope`  \frac{m}{s^2} $$

### Exporting data as csv file. 
```{r}
write.table(data, "./ErrorAnalysis.csv")
```

## Part2: Acceleration of a Turbine-Powered Glider

Here's the collected data
```{r}
time <- seq(0,1.4, by=0.1)
Position<- c(0,0.23,0.428, 0.59, 0.72, 0.815, 0.88, 0.91, 0.905, 0.87,0.8, 0.695,0.56,0.385, 0.18)
Velocity <- c(NA,2.14,1.8,1.46,1.12, 0.8, 0.475, 0.125, -0.2, -0.525, -0.875,-1.2,-1.55,-1.72,NA)
```

### Creating a data table
```{r}
data1 <- data.frame(time, Position, Velocity)
data1
```

### Plotting Position vs. Time
```{r}
plot(data1$time, data1$Position,main="Position vs. Time", xlab="Time", ylab="Position" )
```

### Plotting Velocity vs. Time
```{r}
fit3<- lm(Velocity~time, data1)
plot(data1$time, data1$Velocity, main="Velocity vs. Time", xlab="Time", ylab="Velocity")
abline(fit3)
```

### Fitting the linear regression model and extracting the coefficients
```{r}
summary(fit3)
summary(fit3)$coef
slope1 <- round(summary(fit3)$coef[2,1],3)
intercept1<- round(summary(fit3)$coef[1,1],3)
errorintercept1 <- round(summary(fit3)$coef[1,2],3)
errorslope1 <- round(summary(fit3)$coef[2,2],3)
```


## Plots using ggplot
### Position vs. Time
```{r, message=FALSE, warning=FALSE}
g3<- ggplot(data1, aes(x=time, y=Position))+
        geom_point(size = 2, colour = "red", alpha=0.5)+
        xlab("Time")+
        ylab("Position") +
        ggtitle("Position vs. time") 
        
        
g3
```

###Velocity vs. Time
```{r, message=FALSE, warning=FALSE}
g4 <- ggplot(data1, aes(x=time, y=Velocity))+
        geom_smooth(method = "lm", colour = "black") + 
        xlab("Time")+
        ylab("Velocity") +
        ggtitle("Velocity vs. time") + 
        geom_point(size = 2, colour = "blue", alpha=0.5)
        
g4
```

$$ v_o= `r intercept1` \pm `r errorintercept1`  \frac{m}{s} $$
$$ a= `r slope1` \pm `r errorslope1`  \frac{m}{s^2} $$