---
output:
  html_document: default
  pdf_document: default
---
```{r date, echo=FALSE, message=FALSE, warning=FALSE}
library(knitr)
library(ggplot2)
today <- Sys.Date()
today<- format(today, format="%B %d %Y")
```

---
title: "Lab 5:Modified Atwood's Machine and Newton's 2nd Law"
date: `r today`
output: pdf_document
---

```{r , include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Lab 5:Modified Atwood's Machine and Newton's 2nd Law

```{r , echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
t <- seq(0,0.55, by=0.05)
x<- c(0.0, 0.01,0.025,0.045, 0.07, 0.105, 0.145, 0.19, 0.24, 0.3, 0.36, 0.43)
vx <- c(NA,0.25, 0.35,0.45,0.6, 0.75, 0.85, 0.95, 1.1, 1.2, 1.3,NA)
y <- c(0.425,0.42,0.41, 0.39, 0.365, 0.34, 0.3, 0.265, 0.215, 0.16, 0.1, 0.04)
vy<- c(NA,-0.15, -0.3, -0.45, -0.5, -0.65, -0.75, -0.85, -1.05, -1.15, -1.2, NA)

```


```{r, echo=FALSE, comment=" "}
lab5 <- data.frame(t,x,y,vx, vy)
lab5
```
### Horizontal Mass
```{r ,echo=TRUE}
x1 <- ggplot(lab5, aes(t, x)) +
         geom_point(col="red") +
         theme(plot.title = element_text(hjust=0.5)) +
         labs(title = "Displacement of the horizontal mass", x="Time", y = "Position")+
         theme(plot.title = element_text(color="blue", size=14, face="bold"))

x1
```
\newpage
Coefficients of the horizontal mass
```{r x,echo=TRUE,warning=FALSE, comment=" "}
xt <- lm(vx~t, lab5)
summary(xt)$coef
slope1 <- round(summary(xt)$coef[2,1],3)
intercept1<- round(summary(xt)$coef[1,1],3)
ei1 <- round(summary(xt)$coef[1,2],3)
es1 <- round(summary(xt)$coef[2,2],3)
```



```{r vx,echo=TRUE, warning=FALSE}
v1<- ggplot(lab5, aes(t, vx)) +
        geom_smooth(method='lm', formula=y~x, se=FALSE)+
        geom_point(col="red") +
        theme(plot.title = element_text(hjust=0.5)) +
        labs(title = "Velocity of horizontal mass", x="Time", y = "Velocity")+
        theme(plot.title = element_text(color="blue", size=14, face="bold"))
v1

```

Initial velocity of the horizontal mass  
$$ v_x = `r intercept1` \pm `r ei1` \frac{m}{s} $$
Acceleration of the horizontal mass
$$ a_x = `r slope1` \pm `r es1` \frac{m}{s^2} $$

### Hanging Mass

```{r y1,echo=TRUE}
y1 <- ggplot(lab5, aes(t, y)) +
         geom_point(col="green") +
         theme(plot.title = element_text(hjust=0.5)) +
         labs(title = "Displacement of the hanging mass", x="Time", y = "Position")+
         theme(plot.title = element_text(color="blue", size=14, face="bold"))

y1
```

Coefficients of the vertical mass
```{r y,echo=TRUE,warning=FALSE, comment=" "}
yt <- lm(vy~t, lab5)
summary(yt)$coef
slope2 <- round(summary(yt)$coef[2,1],3)
intercept2<- round(summary(yt)$coef[1,1],3)
ei2 <- round(summary(yt)$coef[1,2],3)
es2 <- round(summary(yt)$coef[2,2],3)
```

```{r vy,echo=TRUE, warning=FALSE}
v2<- ggplot(lab5, aes(t, vy)) +
        geom_smooth(method='lm', formula=y~x, se=FALSE)+
        geom_point(col="green") +
        theme(plot.title = element_text(hjust=0.5)) +
        labs(title = "Velocity of the hanging mass", x="Time", y = "Velocity")+
        theme(plot.title = element_text(color="blue", size=14, face="bold"))
v2

```

Initial velocity of the vertical mass  
$$ v_y = `r intercept2` \pm `r ei2` \frac{m}{s} $$
Acceleration of the vertical mass
$$ a_y = `r slope2` \pm `r es2` \frac{m}{s^2} $$